Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
Figure

@@

>>>>

\begin{figure}[t]
  \centering\scriptsize
  \setlength{\figurewidth}{.26\textwidth}
  \setlength{\figureheight}{\figurewidth}
  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
  %
  \begin{minipage}[t]{.17\textwidth}
    \raggedleft
    \pgfplotsset{ylabel=NLPD}
    \input{./fig/australian.tex}
  \end{minipage}
  \hfill
%  \begin{minipage}[t]{.16\textwidth}
%    \raggedleft
%    \input{./fig/breast_cancer.tex}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[t]{.16\textwidth}
%    \raggedleft
%    \input{./fig/ionosphere.tex}
%  \end{minipage}
%  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/glass.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/vehicle.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/waveform.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/digits.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/satellite.tex}
  \end{minipage}\\%[1em]
  %
  % Show the legend separately
  %\pgfplotsset{hide axis,legend columns=-1,legend style={draw=none,column sep=1ex,font=\Large}}
  %\input{./fig/uci-legend.tex}\\[-2.5em]
  \caption{Comparison of convergence in terms of  negative log-predictive density (NLPD) as averages over 10-fold cross-validation runs, on UCI classification tasks.}
  \label{fig:uci}
  %\vspace*{-6pt}
\end{figure}

@@

\begin{figure}
  \raggedleft\scriptsize
  \setlength{\figurewidth}{\textwidth}
  \setlength{\figureheight}{.55\figurewidth}
  %\pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=north east}}
  %\pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
  %\def\our{{\sc sfr} (ours)}
  \input{./fig/MNIST_acc.tex}
  \caption{Foo}
  \label{fig:mnist}
\end{figure}
